The necessity of hypermedia RDF and an approach to achieve it

### 2012-04-12 eswc-2012/workshop2.tex
Add ref for atompub
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@220 43ef1190-90fd-4dd7-a769-d0121f02b80e
POST in relation to graph store
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@221 43ef1190-90fd-4dd7-a769-d0121f02b80e

% TODO:
% References
% POST in relation to graph store
% Weakness of RDF
% Reformulate something on SPARQL about enabling
% More writing around factors?

@@

AtomPub %TODO: ref
is a widely cited as a good example of a RESTful protocol and
we note that it has a single service endpoint. From there, you can
navigate to what you need. This motivates the first discussion topic
of this paper:

@@

@@

Also note the \texttt{hm:mergedInto} term was motivated by that POST
operations in this specification results in an RDF Merge of the
payload into the named graph.

>>>>

% TODO:
% POST in relation to graph store
% Weakness of RDF
% Reformulate something on SPARQL about enabling
% More writing around factors?

@@

The Atom Publishing Protocol\cite{atompub} is a widely cited as a good
example of a RESTful protocol and we note that it has a single service
endpoint. From there, you can navigate to what you need. This
motivates the first discussion topic of this paper:

@@

This term is motivated by that POST operations in \cite{graphstore} is
specified to results in an RDF Merge of the payload into the named
graph. Amongst other possibilities is a union of graphs.

@@
